\documentclass[11pt,a4paper]{article}

\setlength{\headsep}{.6cm}
\setlength{\textwidth}{16.5cm}
\setlength{\textheight}{26.5cm}
\setlength{\voffset}{-2.5cm}
\setlength{\hoffset}{-.28cm}
\setlength{\oddsidemargin}{0cm}
\setlength{\evensidemargin}{0cm}


\usepackage[utf8]{inputenc}
\usepackage{color, amsfonts, amsmath, graphicx, multicol} 
\definecolor{linkcolor}{rgb}{0,0,0.6} 
\usepackage[pdftex,
colorlinks   = true,
pdfstartview = FitV,
linkcolor    = linkcolor,
citecolor    = linkcolor,
urlcolor     = linkcolor,
hyperindex   = true,
hyperfigures = false]
{hyperref}
\renewcommand\refname{}

\begin{document}


% ===============================================================================


\thispagestyle{empty}

\begin{multicols}{2}

	\begin{flushleft}
	{\Large
		{\bf\'Etienne Fodor}
	}

		{\large Oppenheimer Research Fellow}

		\vskip.1cm
		e.fodor@damtp.cam.ac.uk

		\url{https://efodorphysics.github.io}
	\end{flushleft}

	\columnbreak
	\begin{flushright}
		DAMTP

		Centre for Mathematical Sciences

		University of Cambridge
		
		Wilberforce Road, CB3 0WA
	\end{flushright}

\end{multicols}


% ===============================================================================

\noindent{\large\bf Education and scientific positions}
\vskip.15cm
\hrule
\vskip.3cm

\noindent
2016--20 \hskip.5cm{\bf Postdoctoral Research Associate}, DAMTP, University of Cambridge

\vskip.1cm
\noindent
2013--16 \hskip.5cm{\bf PhD in Theoretical Physics}, Universit\'e Paris Diderot $|$ Summa cum laude

\hskip1.4cm{\it Tracking nonequilibrium in living matter and self-propelled systems}

\hskip1.4cm Main topics $|$ Nonequilibrium statistical mechanics, Biophysics, Active matter

\hskip1.4cm Supervisors \hskip.05cm $|$ Paolo Visco, Frédéric van Wijland

\vskip.1cm
\noindent
2012--13 \hskip.5cm{\bf Master in Physics -- 2\textsuperscript{nd} year}, \'Ecole Normale Supérieure de Paris

\hskip1.4cm ICFP - Macroscopic Physics and Complexity

\vskip.1cm
\noindent
2011--12 \hskip.5cm{\bf Agrégation de Physique}, \'Ecole Normale Supérieure de Cachan

\hskip1.4cm Competitive training for teaching Physics at College level

\vskip.1cm
\noindent
2010--11 \hskip.5cm{\bf Master in Physics -- 1\textsuperscript{st} year}, \'Ecole Normale Supérieure de Lyon

\vskip.1cm
\noindent
2009--10 \hskip.5cm{\bf Bachelor in Physics}, \'Ecole Normale Supérieure de Lyon


% ===============================================================================


\vskip.25cm
\noindent{\large\bf Research and teaching experience}
\vskip.15cm
\hrule
\vskip.3cm

\noindent
Since 2017 \hskip.1cm {\bf PhD co-supervision}, DAMTP, University of Cambridge

\hskip1.4cm Students $|$ Oyvind Borthne, Timothy Ekeh


% -------------------------------------------------------------------------------

\vskip.1cm
\noindent
2019--20 \hskip.5cm{\bf Part III project supervision}, DAMTP, University of Cambridge $|$ 8 months

\hskip1.4cm Part III student $|$ Jacob W. Knight (University of Cambridge) $|$ BP Nevill Mott Prize


% -------------------------------------------------------------------------------

\vskip.1cm
\noindent
2019 \hskip1.1cm{\bf Research visit} James Franck Institute, University of Chicago $|$ 2 weeks

\hskip1.4cm Host researcher $|$ Suriyanarayanan Vaikuntanathan

% -------------------------------------------------------------------------------

\vskip.1cm
\noindent
2017--18 \hskip.5cm{\bf Part III project supervision}, DAMTP, University of Cambridge $|$ 8 months

\hskip1.4cm Part III student $|$ Timothy Ekeh (University of Cambridge)

% -------------------------------------------------------------------------------

\vskip.1cm
\noindent
2016--17 \hskip.5cm{\bf Internship supervision}, DAMTP, University of Cambridge $|$ 5 months

\hskip1.4cm Master student $|$ David Martin (\'Ecole Normale Supérieure de Paris)

% -------------------------------------------------------------------------------

\vskip.1cm
\noindent
2015--16 \hskip.5cm{\bf Research visit}, YITP, Kyoto University $|$ 2 months/year

\hskip1.4cm Host researcher $|$ Hisao Hayakawa

% -------------------------------------------------------------------------------

\vskip.1cm
\noindent
2013--16 \hskip.5cm{\bf Tutorials in medical Physics}, Universit\'e Paris Diderot $|$ 64 hours/year

% -------------------------------------------------------------------------------

\vskip.1cm
\noindent
2013 \hskip1.1cm{\bf Master internship -- 2\textsuperscript{nd} year}, Universit\'e Paris Diderot $|$ 16 weeks

\hskip1.4cm Supervisors $|$ Paolo Visco, Frédéric van Wijland

% -------------------------------------------------------------------------------

\vskip.1cm
\noindent
2012--13 \hskip.5cm{\bf Physics tutorials at College level}, Lycée Fénelon, Paris $|$ 23 hours

% -------------------------------------------------------------------------------

\vskip.1cm
\noindent
2011 \hskip1.1cm{\bf Master intership -- 1\textsuperscript{st} year}, University of Oxford $|$ 12 weeks

\hskip1.4cm Supervisors $|$ Adam S. Wyatt, Ian A. Walmsley

% -------------------------------------------------------------------------------

\vskip.1cm
\noindent
2010--11 \hskip.5cm{\bf Physics tutorials at College level}, Lycée la Martinière Monplaisir, Lyon $|$ 60 hours

% -------------------------------------------------------------------------------

\vskip.1cm
\noindent
2010 \hskip1.1cm{\bf Bachelor internship}, Universit\'e de Gen\`eve $|$ 8 weeks

\hskip1.4cm Supervisors $|$ Jérôme Extermann, Luigi Bonacina, Jean-Pierre Wolf


% ===============================================================================


\vskip.25cm
\noindent{\large\bf Scholarships, fellowships and awards}
\vskip.15cm
\hrule
\vskip.3cm

\noindent
2017--20 \hskip.5cm{\bf Oppenheimer Research Fellowship}, University of Cambridge

\hskip1.4cm{\bf Junior Research Fellowship}, St Catharine's College, Cambridge 

\vskip.1cm
\noindent
2017 \hskip1.1cm{\bf PhD prize}, Institut des Systèmes Complexes, Paris ($3^\text{rd}$ prize)

\hskip1.4cm {\bf Best talk prize}, SIAM-IMA Annual Conference, University of Cambridge

\vskip.1cm
\noindent
2015 \hskip1.1cm{\bf Best talk prize}, Active Liquids Conference, Lorentz Center, Leiden University

\vskip.1cm
\noindent
2013--16 \hskip.5cm{\bf Teaching Assistantship}, Universit\'e Paris Diderot

\hskip1.4cm {\bf PhD Scholarship}, \'Ecole Normale Supérieure de Cachan

\vskip.1cm
\noindent
2011--13 \hskip.5cm{\bf Master Scholarship}, \'Ecole Normale Supérieure de Cachan


% ===============================================================================


\newpage
\thispagestyle{empty}
\noindent{\large\bf Scientific production}
\vskip.15cm
\hrule
\vskip.3cm

\noindent
{\bf [20]} T. Ekeh, M. E. Cates, and \'E. Fodor, {\it Thermodynamic cycles with active matter}, to appear in arXiv

\vskip.1cm
\noindent
{\bf [19]} \'E. Fodor, T. Nemoto, and S. Vaikuntanathan, {\it Dissipation controls transport and phase transitions in active fluids: Mobility, diffusion and biased ensembles}, New J. Phys. {\bf 22}, 013052 (2020)

\vskip.1cm
\noindent
{\bf [18]} P. Pietzonka, \'E. Fodor, C. Lohrmann, M. E. Cates, and U. Seifert, {\it Autonomous engines driven by active matter: Energetics and design principles}, Phys. Rev. X {\bf 9}, 041032 (2019)

\vskip.1cm
\noindent
{\bf [17]} L. Tociu, \'E. Fodor, T. Nemoto, and S. Vaikuntanathan, {\it How dissipation constrains fluctuations in nonequilibrium liquids: Diffusion, structure and biased interactions}, Phys. Rev. X {\bf 9}, 041026 (2019)

\vskip.1cm
\noindent
{\bf [16]} V. Démery and \'E. Fodor, {\it Driven probe under harmonic confinement in a colloidal bath}, J. Stat. Mech. {\bf 2019}, 033202 (2019)

\vskip.1cm
\noindent
{\bf [15]} T. Nemoto, \'E. Fodor, M. E. Cates, R. L. Jack, and J. Tailleur, {\it Optimizing active work: Dynamical phase transitions, collective motion and jamming}, Phys. Rev. E {\bf 99}, 022605 (2019)

\vskip.1cm
\noindent
{\bf [14]} \'E. Fodor, H. Hayakawa, J. Tailleur, and F. van Wijland, {\it Non-Gaussian noise without memory in active matter}, Phys. Rev. E {\bf 98}, 062610 (2018)

\vskip.1cm
\noindent
{\bf [13]} \'E. Fodor and M. Cristina Marchetti, {\it The statistical physics of active matter: From self-catalytic colloids to living cells}, Physica A {\bf 504}, 106 (2018)

\vskip.1cm
\noindent
{\bf [12]} D. Martin, C. Nardini, M. E. Cates, and \'E. Fodor, {\it Extracting maximum power from active colloidal heat engines}, EPL (Europhys. Lett.) {\bf 121}, 60005 (2018) $|$ Editor's choice $|$ Highlights of 2018

\vskip.1cm
\noindent
{\bf [11]} W. W. Ahmed,$^*$ \'E. Fodor,$^*$ M. Almonacid,$^*$ M. Bussonnier, N. S. Gov, M.-H. Verlhac, P. Visco, F. van Wijland, and T. Betz, {\it Active mechanics reveal molecular-scale force kinetics in living oocytes}, Biophys. J. {\bf 114}, 1667 (2018)

\vskip.1cm
\noindent
{\bf [10]} \'E. Fodor,$^*$ V. Mehandia,$^*$ J. Comelles, R. Thiagarajan, N. S. Gov, P. Visco, F. van Wijland, D. Riveline, {\it Spatial fluctuations at vertices of epithelial layers: Quantification of regulation by Rho pathway}, Biophys. J. {\bf 114}, 939 (2018)

\vskip.1cm
\noindent
{\bf [9]} C. Nardini, \'E. Fodor, E. Tjhung, F. van Wijland, J. Tailleur, and M. E. Cates, {\it Entropy production in field theories without time-reversal symmetry: Quantifying the non-equilibrium character of active matter}, Phys. Rev. X {\bf 7}, 021007 (2017)

\vskip.1cm
\noindent
{\bf [8]} \'E. Fodor,$^*$ W. W. Ahmed,$^*$ M. Almonacid,$^*$ M. Bussonnier, N. S. Gov, M.-H. Verlhac, T. Betz, P. Visco, and F. van Wijland, {\it Nonequilibrium dissipation in living oocytes}, EPL (Europhys. Lett.) {\bf 116}, 30008 (2016)

\vskip.1cm
\noindent
{\bf [7]} \'E. Fodor, C. Nardini, M. E. Cates, J. Tailleur, P. Visco, and F. van Wijland, {\it How far from equilibrium is active matter?}, Phys. Rev. Lett. {\bf 117}, 038103 (2016) $|$ Editor's suggestion $|$ Physics (2016)

\vskip.1cm
\noindent
{\bf [6]} \'E. Fodor, H. Hayakawa, P. Visco, and F. van Wijland, {\it Active cage model of glassy dynamics}, Phys. Rev. E {\bf 94}, 012610 (2016)

\vskip.1cm
\noindent
{\bf [5]} E. Ben Isaac, \'E. Fodor, P. Visco, F. van Wijland, and N. S. Gov, {\it Modeling the dynamics of a tracer particle in an elastic active gel}, Phys. Rev. E {\bf 92}, 012716 (2015)

\vskip.1cm
\noindent
{\bf [4]} W. W. Ahmed, \'E. Fodor, and T. Betz, {\it Active cell mechanics: Measurement and theory}, Biochimica et Biophysica Acta - Mol. Cell Res. {\bf 1853}, 3083 (2015)

\vskip.1cm
\noindent
{\bf [3]} \'E. Fodor,$^*$ M. Guo,$^*$ N. S. Gov, P. Visco, D. A. Weitz, and F. van Wijland, {\it Activity-driven fluctuations in living cells}, EPL (Europhys. Lett.) {\bf 110}, 48005 (2015) $|$ Editor's choice $|$ Europhysics News 46/5 (2015)

\vskip.1cm
\noindent
{\bf [2]} \'E. Fodor, D. S. Grebenkov, P. Visco, and F. van Wijland, {\it Generalized Langevin equation with hydrodynamic backflow: Equilibrium properties}, Physica A {\bf 422}, 107 (2015)

\vskip.1cm
\noindent
{\bf [1]} \'E. Fodor, K. Kanazawa, H. Hayakawa, P. Visco, and F. van Wijland, {\it Energetics of active fluctuations in living cells}, Phys. Rev. E {\bf 90}, 042724 (2014)

\vskip.1cm
\noindent
$^*$ Equal contribution of these authors to this work


% ===============================================================================


\newpage
\thispagestyle{empty}
\noindent{\large\bf Scientific presentations, organized events, and review service}
\vskip.15cm
\hrule
\vskip.3cm

\noindent
{\bf Invited conference talks}

\vskip.1cm
\noindent
2020 \hskip1.1cm {\it Japan-France Joint Seminar}, Kyoto University

\hskip1.4cm {\it Frontiers in Non-Equilibrium Physics Workshop}, Kyoto University

\vskip.1cm
\noindent
2018 \hskip1.1cm {\it Why Measure Entropy Production?}, Princeton University

\hskip1.4cm {\it Active Matter Session}, University of California, Berkeley


% -------------------------------------------------------------------------------


\vskip.2cm
\noindent
{\bf Contributed conference talks}

\vskip.1cm
\noindent
2020 \hskip1.1cm {\it Motile Active Matter Conference}, Bonn

\vskip.1cm
\noindent
2019 \hskip1.1cm {\it StatPhys -- Out-of-equilibrium aspects}, Buenos Aires

\hskip1.4cm {\it International Soft Matter Conference}, Edinburgh

\hskip1.4cm {\it Statistical Physics of Complex Systems}, Nordita, Stockholm

\vskip.1cm
\noindent
2018 \hskip1.1cm {\it Nonequilibrium Collective Dynamics}, Technische Universität Berlin

\hskip1.4cm {\it Fundamental Problems in Active Matter}, Aspen Center for Physics

\vskip.1cm
\noindent
2017 \hskip1.1cm {\it SIAM-IMA Annual Conference}, University of Cambridge

\hskip1.4cm {\it Edwards Centre Mini Conference}, University of Cambridge

\hskip1.4cm {\it Open Statistical Physics}, Milton Keynes

\vskip.1cm
\noindent
2016 \hskip1.1cm {\it StatPhys -- Biological Physics}, Lyon

\hskip1.4cm {\it Non-Gaussian Workshop}, Kyoto University

\vskip.1cm
\noindent
2015 \hskip1.1cm{\it Lorentz Center -- Active Liquids}, Leiden University

\vskip.1cm
\noindent
2014 \hskip1.1cm {\it Condensed Matter in Paris}, Universit\'e Paris Descartes

\hskip1.4cm {\it ESPCI -- Journées de Physique Statistique}, Paris


% -------------------------------------------------------------------------------


\vskip.2cm
\noindent
{\bf Invited seminars}

\vskip.1cm
\noindent
2020 \hskip1.1cm{\it Department of Physics}, University of Bath

\vskip.1cm
\noindent
2019 \hskip1.1cm{\it ICTP -- Quantitative Life Sciences Group}, Trieste

\hskip1.4cm {\it James Franck Institute -- Department of Chemistry}, University of Chicago

%\hskip.4cm {\it Gordon Research Seminars -- Soft Matter}, Colby-Sawyer College, New London $|$ Poster

\hskip1.4cm {\it Physics of Living Systems}, Massachusetts Institute of Technology

\hskip1.4cm {\it Physics and Materials Science Research Unit}, University of Luxembourg

\hskip1.4cm {\it Institute of Physics -- Computational Soft Matter}, University of Amsterdam

\vskip.1cm
\noindent
2018 \hskip1.1cm{\it LiPhy Laboratory}, Université Grenoble Alpes

\hskip1.4cm {\it Charles Coulomb Laboratory}, Université de Montpellier

\hskip1.4cm {\it ESPCI -- Gulliver Laboratory}, Paris

\hskip1.4cm {\it St Catharine's College -- Graduate Research Seminars}, Cambridge

\hskip1.4cm {\it Research Colloquium Series}, California State University,	 Fullerton


\vskip.1cm
\noindent
2017 \hskip1.1cm{\it DAMTP -- Soft Matter Seminar}, University of Cambridge

%\hskip.4cm {\it Fundamental Problems in Statistical Physics summer school}, Bruneck $|$ Poster

\hskip1.4cm {\it DAMTP -- BioLunch Seminar}, University of Cambridge

\vskip.1cm
\noindent
2016 \hskip1.1cm{\it School of Mathematical Sciences}, Queen Mary University of London

\hskip1.4cm {\it DAMTP -- Soft Matter Seminar}, University of Cambridge

\hskip1.4cm {\it MSC Laboratory Seminar}, Universit\'e Paris Diderot

\hskip1.4cm {\it Yukawa Institute for Theoretical Physics}, Kyoto University


\vskip.1cm
\noindent
2015 \hskip1.1cm{\it LiPhy Laboratory}, Universit\'e Grenoble Alpes

\hskip1.4cm {\it Physics-Biology Interface Seminar}, Universit\'e Paris Sud

\hskip1.4cm {\it DAMTP -- Soft Matter Seminar}, University of Cambridge

\hskip1.4cm {\it Yukawa Institute for Theoretical Physics}, Kyoto University

%\hskip.4cm  {\it Kyoto Winter School for Statistical Mechanics}, Kyoto University

\vskip.1cm
\noindent
2014 \hskip1.1cm{\it MSC Laboratory -- Physique du vivant}, Universit\'e Paris Diderot

\hskip1.4cm {\it MSC Laboratory -- Theory Group}, Universit\'e Paris Diderot


% -------------------------------------------------------------------------------


\vskip.2cm
\noindent
{\bf Organized events}

%\vskip.1cm
%\noindent
%Since 2018 \hskip.1cm{\it Statistical Physics and Soft Matter Seminars}, DAMTP, University of Cambridge

\vskip.1cm
\noindent
2019 \hskip1.1cm {\it Colloids as a Toolbox for Statistical Mechanics}, University of Cambridge

\vskip.1cm
\noindent
2018 \hskip1.1cm {\it World Congress of Biomechanics -- Non-equilibrium Biomechanics session}, Dublin


% -------------------------------------------------------------------------------


\vskip.2cm
\noindent
{\bf Review service}
\hskip.1cm
Nat. Phys., Phys. Rev. (Letters, X, E), J. Stat. Mech., New J. Phys., EPL


% ===============================================================================


\end{document}


% -------------------------------------------------------------------------------


